### 2023-05-09 response-to-audit-report.md

> **File `specification-v3-rc1.pdf`, Section `2.1.8 State and Environment`, page *14***
>
> The meaning of the data types `IntervalError` and `IntervalResult` needs to be explained.

These types were properly documented in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

@@

### 2.2.6 Incomplete explanation for `TransactionOutput` *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.1 Compute Transaction`, page *15***
>
> The meaning of the data type `TransactionOutput` needs to be explained. More generally, the meaning of the return types of most functions has to be explained. Currently, the meaning can only be inferred from looking at how the types are used, which makes it harder to identify if they are used as intended.
>
> The purpose of these types needs to be made explicit so it can be checked if the code is doing what is intended.

This type was properly documented in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

@@

### 2.2.7 Code snippets switch languages *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.1 Compute Transaction`, page *15***
>
> The specification changes from using Isabelle to using Haskell henceforth. Making the reader aware of the criteria for the language change would help maintaining the document.

The cause of this problem was that initially we had the Isabelle code separated from the documentation generation and we could not find a way to display the Isabelle code, so we showed the exported Haskell instead. We agree that it is confusing so we refactored to a literate programming style in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

@@

### 2.2.8 Repeated definition of `IntervalResult` *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Sections `2.1.8 State and Environment, 2.2.2 Fix Interval`, pages *14, 16***
>
> The `IntervalResult` type is defined twice in the specification. One should be removed.

We removed the extra definition in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

### 2.2.9 Poorly named variable `newAccount` *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.6 Reduce Contract Step`, page *19***
>
> In the implementation of the function `reduceContractStep`, the variable `newAccount` should be named `newAccounts`.

We renamed as suggested in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

@@

We renamed as suggested in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

### 2.2.11 Inaccurate specification of `giveMoney` *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.9 Utilities`, page *22***
>
> It says
>
> > The *giveMoney* function transfers funds internally between accounts.
>
> which is not accurate. It should say instead
>
> > The *giveMoney* function deposits funds to an internal account.
>
> This function is confusing in that it takes the account identifier of the paying account which is not used for anything other than filling a field in the returned value.

This function is confusing, we will likely to remove it in a future release.

@@

### 2.2.12 Redundant evaluation in `addMoneyToAccount` *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.9 Utilities`, page *22***
>
> `addMoneyToAccount` is redundantly evaluating `money <= 0` when invoking `updateMoneyInAccount`. The else branch could be replaced instead with `insert (accId, token) money accountsV`.

We disagree with this observation. The function `updateMoneyInAccount` checks if its money parameter is non-positive, so as to always have accounts with positive balance. The
`addMoneyToAccount` function calls `updateMoneyInAccount` with `balance + money` and checks that `money` is positive. This ensures that `addMoneyToAccount` always increases the assets.

@@

### 2.2.13 Redundant statement regarding addition *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.10 Evaluate Value`, page *24***
>
> It says that addition is associative and commutative. This is true but it is already implied by the equation preceding the statement. Maybe change to
>
> > Note that addition is associative and commutative.
>
> or remove the redundant statement.

The statement was removed in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

### 2.2.14 Missing implementation for negation case of `evalValue` *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.10 Evaluate Value`, page *24***
>
> Negation for `evalValue` does not show the implementation, just one lemma about `NegValue`, which is inconsistent with how other operations are presented.

The way we document `evalValue` was modified in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

@@

### 2.2.15 Missing parentheses in `div` specification *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.10 Evaluate Value`, page *25***
>
> On page 25 formula $$c \neq 0 \Rightarrow c \mathbin{∗} a \mathbin{\mathrm{div}} (c \mathbin{∗} b) = a \mathbin{\mathrm{div}} b$$ needs additional parentheses around the term $c \mathbin{∗} a$, otherwise it can be parsed as $$c \neq 0 \Rightarrow c \mathbin{∗} (a \mathbin{\mathrm{div}} (c \mathbin{∗} b)) = a \mathbin{\mathrm{div}} b$$ which does not hold (Counter-example: $c=2, a=3, b=2$). The lemma `divMultiply` in the file `Semantics.thy` does use extra parentheses around $c \mathbin{∗} a$.

This lemma was removed from the specification and replaced with lemmas that use `evalValue` instead.

@@

### 2.2.16 Unclear division explanation *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.10 Evaluate Value`, page *25***
>
> It says
>
> > Division is a special case because we only evaluate to natural numbers.
>
> The meaning of this statement needs to be further explained, since the arguments of `DivValue` could evaluate to negative numbers.

This was corrected to use `integer` instead of `natural` and further rephrased in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

@@

The way we document `evalValue` was modified in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

### 2.2.18 Missing `evalValue` lemmas in specification *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.10 Evaluate Value`, pages *23--26***
>
> Not all lemmas about `evalValue` are listed in the specification. The absent lemmas include `evalDoubleNegValue`, `evalMulValue`, `evalSubValue`, and all division lemmas.

This section was rewritten and only the Division lemmas are now present, as they are the most relevant ones.

@@

### 2.2.19 Typo in **Use Value** case of `evalValue` *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2.2.10 Evaluate Value`, page *26***
>
> The **Use Value** case mentions `TimeIntervalEnd` instead of `UseValue`.

This section was [rewritten](https://github.com/input-output-hk/marlowe/pull/182) and the issue was fixed.

@@

The function `playTrace` was documented in [PR-182](https://github.com/input-output-hk/marlowe/pull/182) in section 2.2.7.

### 2.2.21 Type parameter discrepancy in `playTrace` *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `3 Marlowe Guarantees`, page *28***
>
> The first parameter of `playTrace` in the specification is `int`, while it is `POSIXTime` in the code. Even though the latter is an alias for the former, it is beneficial to use the `POSIXTime` name both for consistency and readability.

This happened because we were using a type alias, which gets fully expanded when being referenced by the documentation. [PR-182](https://github.com/input-output-hk/marlowe/pull/182) addresses this by making the whole theory in literate programming mode.

@@

The definition in the specification is the exported Haskell code of the Isabelle code. This is a limitation that Isabelle has when importing code from other theories. A possible solution is to change the Accounts positive theory to be literal programming.

### 2.2.25 Misleading or incorrect formula for contract not holding funds *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `3.6.3 Contract Does Not Hold Funds After it Closes`, page *32***
>
> The statement in natural language looks unconnected from the proposed formula. Otherwise, it is unclear how not holding funds forever is a consequence of producing no warnings.

The statement was indeed unconnected from the description. In [PR-186](https://github.com/input-output-hk/marlowe/pull/186) we refactored the guarantees section and now the section "3.2 Finite contracts"
includes the theorem `timedOutTransaction_closes_contract` which shows that after closing a timed-out contract, the accounts are emptied.

@@

### 2.2.26 Different format for lemma statement *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Sections `3.6.2 All Contracts Have a Maximum Time`, page *32***
>
> The lemma is stated using the proof derivation tree format as opposed to the rest of the specification and the Isabelle code.

This was addressed in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

### 2.2.27 Function `isClosedAndEmpty` is unexplained *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `3.6.2 All Contracts Have a Maximum Time`, page *32***
>
> The function `isClosedAndEmpty` needs to be explained.

In [PR-186](https://github.com/input-output-hk/marlowe/pull/186) we added a small explanation; in the future, we will probably expand on this by refactoring the guarantees as literate programming.

@@

### 2.2.28 Top-down definitions *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Section `2`**
>
> In Section 2, the order of definitions is reversed, and the reader is thus faced with functions which call other functions that have not been introduced yet, despite the claim in Section 1.3 that the definitions will be presented bottom-up.

This section was redone in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

@@

### 2.2.29 No mention of Isabelle lemmas in specification *(Severity: Low)*

> **File `specification-v3-rc1.pdf`, Multiple sections ``**
>
> Generally, readability can be improved by mentioning the Isabelle lemma names alongside their statements. This way, it would be much easier to search for the actual Isabelle code and proofs matching the informal specification text, and compare the two.

In [PR-186](https://github.com/input-output-hk/marlowe/pull/186) we added the names of the theories in the specification.

@@

> **Several Isabelle files, several lemmas**
>
> Many Isabelle proof statements and proofs use uninformative variable names. The most common example occurs with variables named $\mathit{x11}, \mathit{x12}$, etc. These inhibit the reader from easily understanding the lemma statements, and often require looking back at constructors to understand what these variables represent.
>
> Some examples of lemmas with these uninformative variable names follow:
> -   in `QuiescentResult.thy`, lemma `reductionLoopIsQuiescent_aux`
> -   in `SingleInputTransactions.thy`, lemmas `beforeApplyAllLoopIsUseless` and\ `applyAllInputsPrefix_aux`
> -   in `ValidState.thy`, lemma `reductionLoop_preserves_valid_state_aux`
> -   in `TimeRange.thy`, lemmas `resultOfReduceIsCompatibleToo`, `resultOfReductionLoopIsCompatibleToo`, `resultOfReduceUntilQuiescentIsCompatibleToo`, `reduceLoop_ifCaseLtCt`, and\ `reduceContractUntilQuiescent_ifCaseLtCt`

We agree with this observation. New lemmas and theories are proven with this recommendation in mind, and some theories were refactored (like the Asset preservation). It will take some time until all theories are in this format.

### 2.3.5 Involved proof of `insert_valid` *(Severity: Low)*

> **File `MList.thy`, theorem `insert_valid`, line *66***
>
> The proof of `insert_valid` sprouts three other lemmas of difficult characterization: `insert_valid_aux`, `insert_valid_aux2`, and `insert_valid_aux3`. These lemmas make assumptions with implications that get in the way of understanding them in isolation.
>
> An alternative to make the proof pieces more reusable is to use instead the following set of lemmas, which also offers insight on how function `insert` interacts with predicates `sorted` and `distinct`:
>
> [. . .]
>
> which then can be combined in the proof of `insert_valid` as follows:
>
> [. . .]
>
> The proofs of the lemmas can be found in […].

We agree that the proposed proof is easier, but the lemma will become obsolete once we replace the custom `MList` with
`HOL-Library/finiteMap`, which addresses other problems found in the report.

@@

### 2.3.6 Repeated verbose expression *(Severity: Low)*

> **File `MoneyPreservation.thy`, lemma `removeMoneyFromAccount_preservation`, line *202***
>
> The expression
>
> ```
>   giveMoney
>     accId
>     (Party p)
>     tok
>     paidMoney
>     (updateMoneyInAccount accId tok (balance - paidMoney) accs)
> ```
>
> is large and used in other lemmas as well. It would need to be moved to a separate function to save the effort of reading it repeteadly.

The `MoneyPreservation` was refactored into Asset preservation and now there is a single reference to `giveMoney`. As mentioned in observation 2.2.11, `giveMoney` is likely to be removed in the future.

@@

This theory was refactored in [PR-161](https://github.com/input-output-hk/marlowe/pull/161) and the lemma was no longer needed.

### 2.3.11 Missing theorem regarding `playTrace` *(Severity: Low)*

> **File `PositiveAccounts.thy`, `playTrace preserves valid and positive state`**
>
> There is no theorem that `playTrace` keeps the state valid and positive when given a state which is valid and positive. This trivially follows from `playTraceAux_preserves_validAndPositive_state` but no such theorem is present.

The valid and positive preservation is needed in lower-level functions so that higher-level functions can use that fact when proving other properties. This makes `playTrace` not needing that proof as it is the highest-level function. The theorem could be useful on its own and might be added in the future.

@@

We agree on this observation and it will addressed in a future refactor of the theory file.

### 2.3.16 Unused and undocumented lemmas *(Severity: Low)*

> **Several Isabelle files, several lemmas**
>
> Some lemmas are never used, and they would need comments motivating their presence:
> 1.  In file `MoneyPreservation.thy`, line 257, lemma `transferMoneyBetweenAccounts_preserves_aux`.
> 2.  In file `QuiescentResult.thy`
>     1.  Line 5, lemma `reduceOne_onlyIfNonEmptyState`
>     2.  Line 153, lemma `reduceContractUntilQuiescent_ifDifferentReduced`
> 3.  In file `PositiveAccounts.thy`, line 66, lemma `positiveMoneyInAccountOrNoAccount_sublist_gtZero`. Furthermore, it is identical to `positiveMoneyInAccountOrNoAccount_gtZero_preservation`, but with an additional assumption `money > 0`.
> 4.  In file `ValidState.thy`
>     1.  Line 9, lemma `valid_state_valid_choices`
>     2.  Line 13, lemma `valid_state_valid_valueBounds`
> 5.  In file `SingleInputTransactions.thy`, line 1214, lemma `traceListToSingleInput_isSingleInput`. It is mentioned in a commented out line in `StaticAnalysis.thy`. Furthermore, the lemma can be expressed more concisely as `$$\llparenthesis \mathit{interval} = \mathit{inte}, \mathit{inputs} = \mathit{inp\_h}\ \#\ \mathit{inp\_t} \rrparenthesis\ \#\ t = \mathit{traceListToSingleInput}\ \mathit{t2} % \mathrel{% \mbox{\fontfamily{cmr}\fontencoding{OT1}\selectfont=}}% \joinrel\Rightarrow\mathit{inp\_t} = []$$`

* Lemma `transferMoneyBetweenAccounts_preserves_aux` was removed in [PR-161](https://github.com/input-output-hk/marlowe/pull/161).
* Lemma `reduceOne_onlyIfNonEmptyState`, `valid_state_valid_choices` were removed in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).
* Lemma `reduceContractUntilQuiescent_ifDifferentReduced` was promoted to a theorem with an explanation in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).
* Lemma `positiveMoneyInAccountOrNoAccount_gtZero_preservation` was removed in favor of `positiveMoneyInAccountOrNoAccount_gtZero_preservation` in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

### 2.3.17 Redundant `reduceContractStep` lemmas *(Severity: Low)*

> **File `MoneyPreservation.thy`, lemma `reduceContractStep_preserves_money_acc_to_acc_aux`, line *310***
>
> This lemma is weaker than `transferMoneyBetweenAccounts_preserves`. If we replace its usage at line 351 with `transferMoneyBetweenAccounts_preserves`, the proof goes through.

This lemma was removed in [PR-161](https://github.com/input-output-hk/marlowe/pull/161).

@@

### 2.3.18 Redundant `transferMoneyBetweenAccounts_preserves` *(Severity: Low)*

> **File `MoneyPreservation.thy`, lemma `reduceContractStep_preserves_money_acc_to_acc`, line *332***
>
> This lemma is weaker than `transferMoneyBetweenAccounts_preserves`. We can replace its usage site in line 376
>
> ```
>   using
>     reduceContractStep_preserves_money_acc_to_acc
>     validAndPositive_state.simps
>    by blast
> ```
>
> with
>
> ```
>   using transferMoneyBetweenAccounts_preserves validAndPositive_state.simps by auto
> ```

This lemma was removed in [PR-161](https://github.com/input-output-hk/marlowe/pull/161).

@@

### 2.3.19 Duplicated lemmas *(Severity: Low)*

> **File `PositiveAccounts.thy`, theorems `computeTransaction_gtZero, accountsArePositive`, lines *257, 369***
>
> These theorems are identical (modulo variable names), and one of them should be removed.
>
> **File `PositiveAccounts.thy, ValidState.thy`, lemma `valid_state_valid_accounts`, lines *381, 5***
>
> This lemma is defined twice, once in each of these files. One of them should be removed.

Lemma `accountsArePositive` was removed in favor of `computeTransaction_gtZero` in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

### 2.3.20 Redundant `computeTransaction` lemmas *(Severity: Low)*

> **File `ValidState.thy`, lemmas `computeTransaction_preserves_valid_state_aux, computeTransaction_preserve_valid_state`, lines *160, 176***
>
> If `computeTransaction_preserves_valid_state_aux` is rewritten to have the same formulation as `computeTransaction_preserves_valid_state`, then the lemma (with the exact same proof) is still accepted, and these lemmas become duplicates of each other. Thus, no auxiliary lemma is needed.

Lemma `computeTransaction_preserves_valid_state_aux` was removed and `computeTransaction_preserve_valid_state` simplified in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

### 2023-05-09 response-to-audit-report.md

### 2.3.21 Complicated formulation of `updateMoneyInAccount_money2_aux` *(Severity: Low)*

> **File `MoneyPreservation.thy`, lemma `updateMoneyInAccount_money2_aux`, line *159***
>
> `updateMoneyInAccount_money2_aux` could be expressed simpler by removing the hypothesis `moneyToPay >= 0`, leaving
>
> [...]
>
> The proof of `updateMoneyInAccount_money2` can then in turn be trivially adjusted so it still works, by changing the step cases
>
> [...]
>
> to
>
> [...]

This lemma was removed in [PR-161](https://github.com/input-output-hk/marlowe/pull/161).

@@

### 2.3.22 Complicated proofs that can be simplified *(Severity: Low)*

> **File `MoneyPreservation.thy`, lemma `moneyInInput_is_positive`, line *53***
>
> The proof could be more general with `apply (cases x; simp)` instead of using `metis`.
>
> **File `MoneyPreservation.thy`, lemma `reductionLoop_preserves_money_NoPayment_not_ReduceNoWarning`, line *434***
>
> This lemma can be proved directly with `metis reductionLoop_preserves_money_NoPayment`, and reversing the order in which the lemmas are defined.
>
> **File `TimeRange.thy`, lemma `inIntervalIdempotentToIntersectInterval`, line *5***
>
> The lemma can use a shorter proof: `apply (cases min2;cases max2;auto) done`.
>
> **File `TimeRange.thy`, lemma `inIntervalIdempotency1, inIntervalIdempotency2`, lines *20, 36***
>
> These lemmas use the `smt` tactic and `metis` where a simpler Isar proof would work, for example:
>
> [...]
>
> **File `SemanticsGuarantees.thy`, `Various lemmas/instantiations`**
>
> Multiple lemmas and `linorder` instantiations in this file repeat auxiliary facts within the proof that are not necessary. For example, in the `linorder` instantiation for `Party`, lines 51--53 state
>
> [...]
>
> This can be rewritten to avoid repeating the fact as
>
> [...]
>
> This pattern appears many times in this file. For example, in the `Party` instantation alone, it is present on lines 51 -- 53, 56 -- 57, 77 -- 80, and 83 -- 84.

These issues were resolved in [PR-168](https://github.com/input-output-hk/marlowe/pull/168) and [PR-169](https://github.com/input-output-hk/marlowe/pull/169)

@@

These observation regarding readability will be addressed when we refactor the theory.

### 2.3.25 Typo with "independet" in multiple lemmas *(Severity: Low)*

> **File `SingleInputTransactions.thy`, lemmas `applyAllLoop_independet_of_acc_error1, applyAllLoop_independet_of_acc_error2`, lines *977, 987***
>
> In both of these lemmas, there is a typo with the word "independet".

This issue was resolved in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

This observation regarding readability will be addressed when we refactor the theory.

### 2.3.28 `playTrace_only_accepts_maxTransactionsInitialState` not written as `theorem` *(Severity: Low)*

> **File `TransactionBound.thy`, lemma `playTrace_only_accepts_maxTransactionsInitialState`, line *316***
>
> This lemma seems like the main result of this file. Assuming it is an important result, we recommend writing it as a `theorem` rather than a `lemma`.

We agree on the observation, and will likely promote it to a theorem in the future.

@@

This observation regarding readability will be addressed when we refactor the theory.

### 2.3.31 Overly specific auxiliary lemma *(Severity: Low)*

> **File `ValidState.thy`, lemma `reductionLoop_preserves_valid_state_aux`, line *73***
>
> This lemma on its own is very specific, and is only used in `reductionLoop_preserves_valid_state`. If possible, we recommend this lemma to be generalized or broken down into smaller lemmas, in order to present the arguments to the reader in smaller pieces.

We agree on this observation and it will be addressed in a future refactoring of the theory file.

@@

### 2.3.32 `playTrace_preserves_valid_state` not written as `theorem` *(Severity: Low)*

> **File `ValidState.thy`, lemma `playTrace_preserves_valid_state`, line *194***
>
> This lemma seems like the main result of this file. Assuming it is an important result, we recommend writing it as a `theorem` instead.

The lemma was promoted to a theorem in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

### 2.3.33 Unnecessary assumptions *(Severity: Low)*

> **File `PositiveAccounts.thy`, lemmas `addMoneyToAccountPositive_match, addMoneyToAccountPositive_noMatch`, lines *12, 23***
>
> The assumptions `$$\forall x\ \mathit{tok}.\ \mathit{positiveMoneyInAccountOrNoAccount}\ x\ \mathit{tok}\ \mathit{accs}$$` in `addMoneyToAccountPositive_match` and `$$\mathit{money > 0}$$` in `addMoneyToAccountPositive_noMatch` are unnecessary.
>
> **File `PositiveAccounts.thy`, lemma `reduceContractStep_gtZero_Refund`, line *93***
>
> The lemma has an assumption that is mostly redundant.
>
> [...]
>
> A stronger lemma would be valid, which results from eliminating the assumption and changing the conclusion to `positiveMoneyInAccountOrNoAccount y tok3 newAccount`.
>
> **File `QuiescentResult.thy`, lemma `reduceContractStepPayIsQuiescent`, line *17***
>
> The assumption $\mathit{cont} = \texttt{Pay}\ \mathit{x21}\ \mathit{x22}\ \mathit{tok}\ \mathit{x23}\ \mathit{x24}$ is unnecessary.
>
> **File `Timeout.thy`, lemma `timedOutReduce_only_quiescent_in_close_When`, line *43***
>
> The assumption $\mathit{minTime}\ \mathit{sta} \leq \mathit{iniTime}$ is unnecessary.
>
> **File `Timeout.thy`, lemma `timedOutReduce_only_quiescent_in_close`, line *122***
>
> The assumption\ $\mathit{minTime}\ \mathit{sta} \leq \mathit{iniTime}$ is unnecessary. However, removing it will require the later proof `timedOutReduceContractLoop_closes_contract` to be adjusted.
>
> **File `Timeout.thy`, lemma `timedOutReduceContractLoop_closes_contract`, lines *170, 173***
>
> The assumptions $\mathit{minTime}\ \mathit{sta} \leq \mathit{iniTime}$ and $\mathit{minTime} \mathit{sta} = \mathit{iniTime}$ are both present. The former is redundant.
>
> **File `TimeRange.thy`, lemma `reduceStep_ifCaseLtCt_aux`, line *234***
>
> The assumption [...] is unnecessary.
>
> **File `ValidState.thy`, lemma `reductionStep_preserves_valid_state_Refund`, line *29***
>
> The assumption [...] is unnecessary.

We removed the unnecessary assumptions in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

The variable was renamed in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

### 2.4.2 Undescriptive name `moneyInPayment` *(Severity: Low)*

> **File `MoneyPreservation.thy`, function `moneyInPayment`, line *5***
>
> The name of the function can be more precise. Perhaps `moneyInPaymentToParty` or `moneyInExternalPayment` would work.

The theory was refactored into `AssetsPreservation` and the function is now called `assetsInExternalPayment`.

@@

### 2.4.3 Typo in section name *(Severity: Low)*

> **File `OptBoundTimeInterval.thy`, line `37`**
>
> Typo in section name: "Interval intesection".

The typo was fixed in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

@@

We agree that it is confusing, and it will be refactored in the future.

### 2.4.6 Variable name discrepancy in `reductionLoop` *(Severity: Low)*

> **File `Semantics.thy`, function `reductionLoop`**
>
> When comparing this function against `specification-v3-rc1.pdf`, different names are used for a let-bound variable. It is `a` in the pdf and `newPayments` in the file `Semantics.thy`. There are similar issues in the function `reduceContractStep` in the equation for the `If` case, and in the function `giveMoney`.

This was an artifact of showing the exported haskell code. It is resolved in [PR-182](https://github.com/input-output-hk/marlowe/pull/182).

@@

The typo was fixed in [PR-168](https://github.com/input-output-hk/marlowe/pull/168).

### 2.4.8 Unclear function name `calculateNonAmbiguousInterval` *(Severity: Low)*

> **File `Semantics.thy`, function `calculateNonAmbiguousInterval`, line *725***
>
> The meaning of the function is not obvious. It needs a comment to explain it.

This function was documented in [PR-168](https://github.com/input-output-hk/marlowe/pull/168) and moved to `TimeRange.thy` in [PR-182](https://github.com/input-output-hk/marlowe/pull/182). The function is not part of the Marlowe spec yet: it is a helper we hope will be useful in the future to construct the transactions.

@@

### 2.4.9 Non-modularized file `SingleInputTransactions.thy` *(Severity: Low)*

> **File `SingleInputTransactions.thy`, `Splitting File`**
>
> This file is very long, and it covers more than just single-input transactions. For instance, about 530 lines at the beginning are rather dedicated to idempotence of certain operations. Then, the lemmas around lines 530 -- 700 focus on "well-foundedness" of the recursion on contract steps. Then there is also a clear block of lemmas about "distributivity" of semantics over transaction lists.
>
> Splitting the module, grouping the related lemmas, would help understanding the relationships between the groups.

We agree with the observation and it will be addressed in a future refactoring.

@@

### 2.4.10 Misleading function names *(Severity: Low)*

> **File `SingleInputTransactions.thy`, function `inputsToTransactions`, line *9***
>
> This function name is not very descriptive of its meaning. It takes a transaction (both a time interval and a list of inputs) and returns a list of transactions at the same interval containing a single input each. A name like `splitTransactionIntoSingleInputTransactions` would convey better what the input and the output are.
>
> Moreover, the code would be cleaner if the function takes a single argument of type `Transaction`, instead of asking the caller to rip apart its fields.
>
> **File `SingleInputTransactions.thy`, function `traceListToSingleInput`, line *18***
>
> This function name is not descriptive of what it does. Perhaps a more telling name could be `splitTransactionsIntoSingleInputTransactions`.
>
> **File `SingleInputTransactions.thy`, function `isSingleInput`, line *1222***
>
> This function should be renamed or repurposed. If renamed, `allAreSingleInput` more accurately reflects the meaning of the function. If repurposed, it should check that a single transaction has a single input, and `all isSingleInput` can be used to express the current behavior.

We agree on the observations, for the moment some simple refactoring and comments were added as part of [PR-180](https://github.com/input-output-hk/marlowe/pull/180/files#diff-638dc578b752590b5f2bace45f1e1ae9e522351f62056e6f92aa272424657b03). Further refactoring and optional renaming might happen in the future.

@@

We agree on this observation and it will addressed in a future refactoring of the theory file.

### 2.4.12 Duplicated `isValidInterval` function *(Severity: Low)*

> **File `TimeRange.thy`, function `isValidInterval`, line *231***
>
> This function duplicates $\texttt{validTimeInterval}$ from $\texttt{OptBoundTimeInterval.thy}$, and the latter has certain additional properties proven about it specifically, so it makes sense to use the latter in both cases.

The function `isValidInterval` was removed in favor of `validTimeInterval` in [PR-168](https://github.com/input-output-hk/marlowe/pull/168/files#diff-9c936a78b5d8eed5683713bb31c59366b2a0794c5f11e9807f7fa61d1b11b7c2L230)

@@

The aforementioned bindings `validateBalances`, `validateInputs`, and `tailCase` have been renamed to `allBalancesArePositive`, `allInputsAreAuthorized`, and `tailCases` in commit [1c96edfe](https://github.com/input-output-hk/marlowe-cardano/commit/1c96edfe7e22ecc499ed75dd175490a4f2427bdc). For historical reasons, `refundOne` has not been renamed. The function `checkScriptOutputAny` is no longer present due to other mitigations made to the validator.

### 2.6.5 Unused functions *(Severity: Low)*

> **File `Several files`, Several functions**
>
> Several functions are unused and perhaps should be removed:
> -   `Semantics.hs:741`: `contractLifespanUpperBound` does not seem to be used anywhere, including tests.
> -   `Semantics.hs:680`: `isClose` is not used in the rest of the codebase (besides checking its behavior via testing). It should either be removed, or comments justifying its existence should be included.
>
> In addition to that, the functions `validateBalances` and `totalBalance` (defined at `Semantics.hs:755` and `:762`) are only used in `Scripts.hs` and never reused, so they should probably be moved to `Scripts.hs`.

Although the validator does not use these functions, off-chain code in other Haskell modules does. For the time being, the `contractLifespanUpperBound` and `isClose` have been retained in `Language.Marlowe.Core.V1.Semantics`. They will be relocated in the future if validator and non-validator code are separated into different modules.
